A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/main_RECOMB.tex
fixed affiliations

%\title{An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs}
\title{A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences}
\author{Vladimir Reinharz$^{2}$, Yann Ponty$^{1}\footnote{To whom correspondence should be addressed}\;$, J\'er\^{o}me Waldisp\"{u}hl$^{2*}$}
\date{$^1$Laboratoire d'Informatique, \'Ecole Polytechnique, Palaiseau, 91120 France $^2$ School of Computer Science \& McGill Centre for Bioinformatics, McGill University, Montr\'eal, Canada H3C 2J7}

>>>>

%\title{An inside-outside algorithms for mutant RNAs with applications to error detections in structured RNAs}
\title{A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences}
\author{Vladimir Reinharz$^{2}$, Yann Ponty$^{1}\footnote{To whom correspondence should be addressed}\;$, J\'er\^{o}me Waldisp\"{u}hl$^{2*}$}
\date{$^1$CNRS/\'Ecole Polytechnique/INRIA AMIB, LIX UMR 7161 X-CNRS, Palaiseau, France $^2$ School of Computer Science \& McGill Centre for Bioinformatics, McGill University, Montr\'eal, Canada H3C 2J7}
